Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-09-21 doc/manuscript/ESSDmanuscript.Rmd
note that calculated variables are not acceptable

>>>>

  - present calculations of all variables that would be useful to IPCC. EFDB requires that data in the database be presented in the original article, and as such cannot accept subsequent calculations. For example, if aboveground biomass and total biomass are presented, but root biomass is not presented, root biomass cannot be subsequently calculated and sent to EFDB.
